---
title: "Penguin Flipper Lengths ANOVA"
author: "Rachel Behm"
date: "November 7, 2018"
output: html_document
---

1. Load packages and read in penguins data
```{r, include= FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

2. Look at and explore data
Our Q: Is there a signif diff for mean in flipper lengths for female chinstrap, gentoo, and adelie penguins near palmer archipelago?
FACTOR: SPECIES
LEVELS: chinstrap gentoo adelie
VARIABLE: flipper length

what are assumptions for 1 way anova?
-dont influence eachother (independent)
-equal variance (lavenes test)
-normality (histo and qq)

WE HAVE TO DO ALL THAT FIRST BEFORE WE DO ANOVA

want to know how many males and females per species (JUST USE TABLE FUNCTION!!)

```{r}
counts <- with(penguins, table(Species, Sex))

View(counts)
#see big sample size so know central limit theorem now lets look at the other stuff
penguinsflip <- penguins %>%
  rename("flipper_length" = "Flipper Length (mm)")


penguins2 <- penguinsflip %>%
  mutate(
    common_name = 
      case_when(
        Species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
        Species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
        Species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adeliae"
      )
  ) %>%
  select(-Species) %>%
  filter(Sex == "FEMALE")
```

```{r}
hists <- ggplot(penguins2, aes(x= flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~common_name, scale = "free")
hists


qqs <- ggplot(penguins2, (aes(sample= flipper_length))) +
  geom_qq(aes(color = common_name)) +
  facet_wrap(~common_name, scale = "free")

qqs

variances <- penguins2 %>%
  group_by(common_name) %>%
  summarize(variance= var(flipper_length))
variances
#yes normal and n>30
```

```{r}

levene_penguin<- leveneTest(flipper_length ~ common_name, data = penguins2)



#null=means across all groups are equal
#at least two group means differ significantly 
penguin_aov <- (aov(flipper_length ~ common_name, data= penguins2))
summary(penguin_aov)

penguin_ph <-TukeyHSD(penguin_aov)
penguin_ph
#null= not different
#alt= yes difference



#ALL OF THEM ARE SIGNIFICANT DIFF FROM EACHOTHER
#"mean flipper length of female penguins differed significantly for all species studied (one way anova, f(df), p<0.001, $|alpha$" =0.05 with post hoc tukes hsd, $\alpha$ = 0.05).

#cant in line code with aov but in onewaytests package it does allow for in line ref


#IF TINY JUST RIGHT <0.001
```

