---
title: "Penguin Flipper Lengths ANOVA"
author: "Rachel Behm"
date: "November 7, 2018"
output: html_document
---

1. Load packages and read in penguins data
```{r, include= FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

2. Look at and explore data
Our Q: Is there a signif diff for mean in flipper lengths for female chinstrap, gentoo, and adelie penguins near palmer archipelago?
FACTOR: SPECIES
LEVELS: chinstrap gentoo adelie
VARIABLE: flipper length

what are assumptions for 1 way anova?
-dont influence eachother (independent)
-equal variance (lavenes test)
-normality (histo and qq)

WE HAVE TO DO ALL THAT FIRST BEFORE WE DO ANOVA

want to know how many males and females per species (JUST USE TABLE FUNCTION!!)

```{r}
counts <- with(penguins, table(Species, Sex))

View(counts)
#see big sample size so know central limit theorem now lets look at the other stuff

penguins2 <- penguins %>%
  mutate(
    common_name = 
      case_when(
        Species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
        Species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
        Species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adeliae"
      )
  ) %>%
  select(-Species) %>%
  filter(Sex == "FEMALE")
```

